### 2018-04-19 Sections/quality_of_service.tex
Ent purif

More concretely, we distribute two Bell pairs of fidelity $F$ between Alice and Bob,
\begin{align}
\ket{\Phi^+_F}_{A,B}\otimes\ket{\Phi^+_F}_{A,B}	
\end{align}
and upon Alice and Bob each only performing local operations between their halves of the two pairs, we wish to be left with a single Bell pair $\ket{\Phi^+_{F'}}$, where \mbox{$F'>F$}.

>>>>

More concretely, we distribute two Bell pairs of fidelity $F$ between Alice and Bob, who perform local operations to reduce them to a single Bell pair of higher fidelity,
\begin{align}
\ket{\Phi^+_F}_{A,B}\otimes\ket{\Phi^+_F}_{A,B} \to \ket{\Phi^+_{F'}}_{A,B},
\end{align}
where,
\begin{align}
F'>F.	
\end{align}
